
---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ch.seco.con.con

Swiss consumer confidence survey data from the State Secretariat for Economic
Affairs (SECO), versioned as an OpenTSI archive. The dataset covers 39 quarterly
time series back to 1972 Q4: the headline 6.3 consumer sentiment index plus 12
component balance series, each available raw (`na`) and seasonally + calendar
adjusted (`csa`), and both as index values and standard deviations.

Data are fetched directly from the SECO swissdata endpoint
(`scheduler.swissdatas.ch`) and versioned on each publication (roughly quarterly).

## Browse Time Series Data

You can use GitHub's ability to render CSV files to explore the datasets
directly in the browser under `data-raw/csv/`.

## Basic Data Consumption via opentimeseries

```r
remotes::install_github("opentsi/opentimeseries")
library(opentimeseries)

# Fetch the headline consumer sentiment index (all vintages)
ts <- read_open_ts(
  series        = "index.ks_i63_index_q.csa",
  remote_archive = "opentsi/ch.seco.con.con"
)
ts
```

Given a unique time series identifier and a GitHub repo,
*opentimeseries* will return a time series and long format `data.table`.

## Basic Usage

```{r, eval=FALSE}
library(opentimeseries)

# Most recent vintage of the headline index
ts <- read_open_ts(
  series        = "index.ks_i63_index_q.csa",
  remote_archive = "opentsi/ch.seco.con.con"
)
```

By specifying a date you can obtain the vintage that was available at that point
in time — useful for real-time forecasting benchmarks.

Because time series data can be revised, storing vintages is important to monitor
data revisions. Here's a quick visual comparison of two vintages:

Currently there is only 1 vintage, hence only one version of this time series will be plotted

```{r}
library(opentimeseries)
library(tsbox)

ts_latest <- read_open_ts(
  series        = "index.ks_i63_index_q.csa",
  remote_archive = "opentsi/ch.seco.con.con"
)
ts_latest$id <- "csa.latest"
ts_plot(ts_latest)
```
